{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-08 wacv_for_review.tex
Figure Updated
Reviewed the entire draft.

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}.

We set up {\it E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target. By setting a transition filter with larger padding size, 
$R_{t}^{L}$, we can recover from potential drifts after the frames we only run the
scale filter. Additionally, we design a translation filter with smaller 
padding size, $R_{t}^{S}$, to better pinpoint target position after the 
frames we only run $R_{t}^{L}$.

{\it Burak: We only explained two kinds of
  filters: translation and scale filter. But we do have two filters
  for target's translation, $R_{t}^{S}$ and $R_{t}^{L}$. Revise the
  the sentence about translation filter with details.}

{\it YoungWoo : In this paragraph, we mention two of the translation
  filters and then we say translation filter needs background whereas
  the scale filter does not.}

{\it Burak: The paragraph I'm referring to begins ``We set up...'' The
  paragraph before this explain what each of the KCFs is for, but
  didn't say why at the next paragraph ``We set up...''}

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail the main idea behind the KCF.

\begin{comment}
{\it Burak: This section does NOT connect to the previous section.}

{\it YoungWoo : I placed EnKCF with traditional and deep features
  section right after EnKCF section. Later, you placed them after the
  Kernelized Correlation Filter section. To me, it makes more sense to
  place them right after the EnKCF section.}

{\it Burak: I don't think that's a good way of arranging this. You
  talked about EnKCF, then KCF should come out before any variants of
  KCF w/ conventional feature and w/ deep features. Otherwise, what is
  the point of having KCF section after you explained all the usage of
  KCF? So, it should EnKCF, KCF, KCF w/ hand-craft features and KCF w/
  deep features. Given this order, two paragraphs before and after
  this didn't connect!}
\end{comment}

@@

The KCF solves essentially the problem of a regression in the form of
the regularization:
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equation \ref{eq:Closedform_RidgeReg} exists. To make the
closed-form solution less complex, an element-wise, multiplication in
frequency domain was proposed for $\hat{w}$:
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of this closed-form solution is proposed to make
it more robust to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized Fourier
domain dual form solution is expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'})))
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $w$ and multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. Specifically,
one can execute an object detection using this kernelized correlation
filter with multi-channel features as
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix. In what follows, we will detail two feature types to be deployed
in KCFs in {\it E}nKCF : (1) hand-crafted features (fHoG + color-naming) and (2) deep convolutional features.

\textbf{{\it E}nKCF with Hand-Crafted Features} 
We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure \ref{fig:Filters}. 
This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
$30$ fps, particularly on the ones without GPU units.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

The translation filter, $R_{t}^{L}$, uses both the fHoG
\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
features to learn the large background area around the target. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. The
color features are also used to make the feature vector more
discriminative. In other words, for the case that the fHoG is the only
feature, the bigger the area for HoG is the more noise the resulting
fHoG feature contains. Adding color information to the feature vector
will make the feature vector more robust to the noises from the
background around the target. However, this is not the case for the
translation filter, $R_{t}^{S}$. This is because the translation filter, {\it target + small background}, 
does not contain much of the background area around the target. Figure
\ref{fig:Filters}(a) shows an example of this translation filter. 
Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
The ROI considered by $R_{s}$ is resized to a smaller template resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c). 
This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
The $R_{s}$ estimates the scale by correlating the filter with three candidate ROIs as detailed in
alg.~\ref{alg:MKCF}.  This increase the complexity from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$. 
To reduce the number of operations, we assign a smaller template size to $R_{s}$. 
This does not degrade the tracking performance due to two reasons: (1) zero padding around the target 
and (2) integration of color features. This way, we keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By reducing the template size of $R_{s}$, fluctuating run-time
performances among $R_{s}$ and, $R_{t}^{L}$ and $R_{t}^{S}$, are avoided which 
is desired in embedded systems.

@@

{\it Burak: What you told me is purely empirical which is fine. But
  you'll have to tell the readers why we wanted to keep the run-time
  complexity of those filters same!}

\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance.

{\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}

@@

{\it YoungWoo : There are three reasons for this: (1) One is CPU and another one is GPU
implementations, I thought it would be more clear to separate them, (2) I do not have 
results on OTB100 dataset with DeepEnKCF. (3) I believe DeepEnKCF is not the main contribution 
of this paper, showing them in the same figure with all the trackers might lead the authors to 
underestimate EnKCF.
 }

This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
devised to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to lost spatial information this layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction
capacity.  Their method first employs the third convolutional layer
features to estimate the response map. In the next stage, the KCF,
concentrating on the second convolutional layer features, is run to
update transition. The third KCF then works on the transition given by
the previous KCF and learns the first convolutional layer features to
update the transition. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, it runs
multiple KCFs in a sequential fashion, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF.

Our {\it E}nKCF framework allows us to exploit different level of
feature encodings with different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger area than
the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it learns less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment scheme is represented as \textit{conv224-VGG} and shown in
Figure~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet since it provides higher spatial
resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied an 
hanning window to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered to avoid target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

\textbf{Particle Filter for Smoothing Transition among KCFs} 
{\it Burak: Does what this section explains still hold good? If what
  this section explains still makes sense, the translation filter,
  $R_{t}^{L}$ doesn't do a good job. Isn't it? If it's not, revise
  this section.}

@@

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}

As explained earlier, the {\it E}nKCF updates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential drifts, we
developed a Bayes filter that incorporates a target's motion to smooth
any intermediate outputs from individual KCFs of the {\it E}nKCF. In
particular, we use a particle filter to estimate the target's image
coordinate based on the {\it E}nKCF's outputs. A particle filter is a
sequential Monte Carlo method that uses a finite number of particles
or samples to estimate the posterior probability density of a state of
the system \cite{thrun2005probabilistic}. In this study, the state
represents a target's pixel coordinates and its motion. In particular,
the state of the particle filter, $X_t$, is represented by $\lbrace x,
y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates
of the target's centroid, $v_x$ and $v_y$ are the estimated velocity
along the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. Then it uses the confidence maps of 
{\it E}nKCF as observation to update the state. The weight of a particle is computed as
\begin{equation}
w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j), 
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
size of the window as that of a confidence map. Alternatively one can
also use the Euclidean distance of particles to the location of
maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
In this section, we evaluate the performance of the proposed {\it E}nKCF
tracker and its variants on the object tracking benchmarks. 
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.
We first evaluate the performance of {\it E}nKCF 
with hand-crafted features as shown in Figure \ref{fig:Filters}.  
With this tracker, we aim at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Also, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets. Finally, we evaluate the Deep{\it E}nKCF, 
{\it E}nKCF with deep features, on the UAV123 dataset to observe how much gain
we can achieve over hand-crafted features.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at $30$fps on a single-board, embedded
system. Given this goal, we used fHoG and color-naming features in an
efficient way in the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. Following the recent trend, we hypothesize 
that the {\it E}nKCF tracker could be improved with deep features trained on ImageNet
dataset. Utilizing pre-trained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. However, as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) learned by the VGGNet
as shown in Figure \ref{fig:Filters_CNN}.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

>>>>

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because, we believe, a correlation filter for learning a
target's translation should include the background of the target to
better discriminate it from its surrounding, and another correlation
filter should focus on the target itself to estimate the right scale
of the target. By setting a transition filter with larger padding
size, $R_{t}^{L}$, we can recover from potential drifts after the
frames we only run the scale filter. Additionally, we design a
translation filter with smaller padding size, $R_{t}^{S}$, to better
localize the position of the target after the frames we only run
$R_{t}^{L}$.

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. On the other
hands, a translation filter, $R_{t}^{L}$, is designed to look at a
larger search area to estimate the target's translation and recover
from any potential drifts. Another translation filter, $R_{t}^{S}$, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail the main idea behind the KCF.

@@

The KCF solves essentially the problem of a regression in the form of
the regularization:
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equation \ref{eq:Closedform_RidgeReg} exists. To make the
closed-form solution less complex, an element-wise, multiplication in
frequency domain was proposed for $\hat{w}$:
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of this closed-form solution is proposed to make
it more robust to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized Fourier
domain dual form solution is expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'})))
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $w$ and multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. Specifically,
one can execute an object detection using this kernelized correlation
filter with multi-channel features as
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

In what follows, we will detail two different types of features used
in {\it E}nKCF : (1) hand-crafted features (fHoG + color-naming) and
(2) deep convolutional features.

\textbf{{\it E}nKCF with Hand-Crafted Features} We, first, use two
conventional hand-crafted features, fHoG (shape)
\cite{felzenszwalb2010object} and color-naming (color)
\cite{li2014scale}. Figure \ref{fig:Filters} shows examples of these
features. This setup of the {\it E}nKCF is designed to perform
tracking on any embedded systems at $30$ fps, ones without GPUs.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

We use both fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} for the large area, translation filter,
$R_{t}^{L}$. This is because the fHoG applied to relatively larger
area is tended to be noisy and less discriminative and adding color
information makes the feature vector for the translation filter,
$R_{t}^{L}$, more robust to noise and more discriminative. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. But,
this is not the case for the small area, translation filter,
$R_{t}^{S}$, because this translation filter does not contain much of
the background area around the target. Figure \ref{fig:Filters}(a)
shows an example of this translation filter. Lastly, we use both fHoG
and color-naming features again for the scale filter,
$R_{s}$. Although we are using the same feature representations for
the scale filter learning relatively smaller area just around the
target, the reason of using two feature sets is sightly different in
that the area to learn is too small for the fHoG to represent the area
well. In addition, the scale filter, explained earlier in the
algorithm \ref{alg:MKCF}, estimates the scale of a target by
correlating it with three candidate ROIs. This search may increase the
run-time complexity of the scale filter from $\mathcal{O}(n\log n)$ to
$\mathcal{O}(3(n\log n))$. To ensure actual filtering operations
practical, we use a smaller template size (i.e., 64$\times n$) for the
scale filter, $R_{s}$. The smaller template size does not degrade the
tracking performance neither because of 1) zero padding around the
target and 2) use of color feature.
\begin{comment}
The ROI considered by $R_{s}$ is resized to a smaller template
resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c).
This leads to less discriminative shape features. To reduce the noise
in $R_{s}$, we concatenate color features.  The $R_{s}$ estimates the
scale by correlating the filter with three candidate ROIs as detailed
in alg.~\ref{alg:MKCF}.  This increases the complexity from
$\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$.  To
reduce the number of operations, we assign a smaller template size to
$R_{s}$.  This does not degrade the tracking performance due to two
reasons: (1) zero padding around the target and (2) integration of
color features. This way, we keep the run-time complexity of the
$R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By reducing the template size of
$R_{s}$, fluctuating run-time performances among $R_{s}$ and,
$R_{t}^{L}$ and $R_{t}^{S}$, are avoided which is desired in embedded
systems.

@@

{\it Burak: What you told me is purely empirical which is fine. But
  you'll have to tell the readers why we wanted to keep the run-time
  complexity of those filters same!}
\end{comment}
\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance. This version of {\it E}nKCF, Deep{\it E}nKCF is
designed to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.
\begin{comment}
{\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}

@@

{\it YoungWoo : There are three reasons for this: (1) One is CPU and another one is GPU
implementations, I thought it would be more clear to separate them, (2) I do not have 
results on OTB100 dataset with DeepEnKCF. (3) I believe DeepEnKCF is not the main contribution 
of this paper, showing them in the same figure with all the trackers might lead the authors to 
underestimate EnKCF.
 }
\end{comment}

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to lost spatial information this layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction
capacity.  Their method first employs the third convolutional layer
features to estimate the response map. In the next stage, the KCF,
concentrating on the second convolutional layer features, is run to
update transition. The third KCF then works on the transition given by
the previous KCF and learns the first convolutional layer features to
update the transition. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, it runs
multiple KCFs in a sequential fashion, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF. Our {\it E}nKCF framework enables us to exploit different
level of feature encodings with different KCFs. The translation
filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger
area than the scale filter, $R_{s}$. Given this, we can assign deeper
feature encodings to $R_{s}$ as it learns less spatial information
than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign the activations of
the fourth convolutional layer features ($26\times26\times128$) to
$R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the
activations of the second layer features
($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
this feature assignment. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. {\it Burak: I don't see any differenciation
  between conv222-VGG and conv224-VGG from the figure, at least labels
  of them.} We use the VGGNet since it provides higher spatial
resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ used an hanning window to avoid distortion caused by FFT operation whereas $R_{s}$ is not filtered {\it Burak: What do you mean by ``not filtered''?} to avoid target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

\textbf{Particle Filter for Smoothing Transition among KCFs}
\begin{comment}
{\it Burak: Does what this section explains still hold good? If what
  this section explains still makes sense, the translation filter,
  $R_{t}^{L}$ doesn't do a good job. Isn't it? If it's not, revise
  this section.}

@@

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead drifts at the
later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $X_t$, represents a target's pixel
coordinates and its velocity, $X_t = \lbrace x, y, v_{x}, v_{y}
\rbrace$, where $x$ and $y$ are the pixel coordinates of the target's
centroid, $v_x$ and $v_y$ are the velocity estimated along the
$x$-axis and $y$-axis. The particle filter predicts, using a constant
velocity motion model, a target's next state by generating a predefined
number of particles. Then it uses the confidence maps of {\it E}nKCF
as observation to update the state. The weight of a particle is
computed as
\begin{equation}
w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j), 
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
size of the window as that of a confidence map. Alternatively one can
also use the Euclidean distance of particles to the location of
maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate the performance of the proposed {\it E}nKCF tracker and
its variants using the object tracking benchmark
datasets. Particularly, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.  We
first evaluate the performance of {\it E}nKCF with two hand-crafted
features, fHoG and color-naming.  With this tracker, we aim at
developing an object tracking algorithm that ``efficiently'' runs on
an embedded system, a drone, for example, in ``high speed,'' $\ge 30$
fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes,
e.g., abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Also, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets. Finally, we evaluate the
Deep{\it E}nKCF, {\it E}nKCF with deep features, on the UAV123 dataset
to observe how much gain we can achieve over hand-crafted features.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at $30$fps on a single-board, embedded
system. To this end, we used two conventional features, fHoG and
color-naming for the {\it E}nKCF. At the same time, we observed that
the feature vectors learned from DNN have been used to improve the
performance of the trackers based on KCF \cite{ma2015hierarchical,
  danelljan2015convolutional}, and some of the single-board, embedded
systems have GPUs. We believe that the performance of the {\it E}nKCF
could be also improved with deep features trained on ImageNet dataset
and like to see how much performance boost we could gain. 
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.
